---
title: "Monoploy Test Cases & Simulation"
author: "Weijie Yuan"
output: pdf_document
---

```{r, error = TRUE}
source("monopoly_new_code.R")
```

\pagebreak

# Part 1: Test Cases

### Test Case 1: Space: Go to Jail

```{r, error = TRUE}
dice <- PresetDice$new(
  rolls = c(3,4),
  verbose = TRUE
)
set.seed(16)
player1 <- Player$new(verbose = TRUE, pos = 24)
monopoly <- SpaceTracker$new(verbose = TRUE)

for(i in 1:1){
  cat("--- Turn", i,"---\n")
  take_turn(player1, monopoly)
  cat("\n")
}

print(setNames(monopoly$counts, 1:40))
```

\pagebreak

### Test Case 2: Chance Card and Doubles Tests: Advance to Go, Reading Railroad, Nearest Railroad, Nearest Utility, No Movement

```{r, error = TRUE}
dice <- PresetDice$new(
  rolls = c(3,4, 4,3, 1,1, 3,4, 5,3),
  verbose = TRUE
)
set.seed(135)
chance <- CardDeck$new(chancedeck, verbose = TRUE)
community <- CardDeck$new(communitydeck, verbose = TRUE)
player1 <- Player$new(verbose = TRUE)
monopoly <- SpaceTracker$new(verbose = TRUE)

for(i in 1:4){
  cat("--- Turn", i,"---\n")
  take_turn(player1, monopoly)
  cat("\n")
}

print(setNames(monopoly$counts, 1:40))
```
\pagebreak

### Test Case 3: Multiple doubles. Community Chest.
```{r, error = TRUE}
dice <- PresetDice$new(
  rolls = c(3,3, 2,2, 2,1, 3,1), verbose = TRUE)

player1 <- Player$new(verbose = TRUE)
monopoly <- SpaceTracker$new(verbose = TRUE)
for(i in 1:2){
  cat("--- Turn", i,"---\n")
  take_turn(player1, monopoly)
  cat("\n")
}

print(setNames(monopoly$counts, 1:40))
```

\pagebreak

### Test Case 4: Doubles three times. Three turns in jail.
```{r, error = TRUE}
dice <- PresetDice$new(
  rolls = c(3,3, 3,3, 3,3, 5,6, 5,6, 5,6),
  verbose = TRUE
)

player1 <- Player$new(verbose = TRUE)
monopoly <- SpaceTracker$new(verbose = TRUE)

for(i in 1:4){
  cat("--- Turn", i,"---\n")
  take_turn(player1, monopoly)
  cat("\n")
}

print(setNames(monopoly$counts, 1:40))
```

\pagebreak

### Test Case 5: After going to Jail, player's turn ends immediately. Rolling doubles while in Jail gets player out of jail.
```{r, error = TRUE}
dice <- PresetDice$new(
  rolls = c(3,3, 1,2, 3,3, 3,4),
  verbose = TRUE
)

player1 <- Player$new(verbose = TRUE, pos = 25)
monopoly <- SpaceTracker$new(verbose = TRUE)

for(i in 1:3){
  cat("--- Turn", i,"---\n")
  take_turn(player1, monopoly)
  cat("\n")
}

print(setNames(monopoly$counts, 1:40))
```

\pagebreak

### Test Case 6: 20 Predetermined Turns

```{r, error = TRUE}
dice <- PresetDice$new(
  rolls = c(6,4, 5,3, 3,5, 4,4, 4,4, 2,2, 4,3, 4,4, 1,4,
            3,4, 1,2, 3,6, 5,4, 5,5, 1,2, 5,4, 3,3, 6,1,
            1,1, 2,3, 5,5, 5,4, 4,1, 2,2, 2,4),
  verbose = TRUE
)
set.seed(2)
chance <- CardDeck$new(chancedeck, verbose = TRUE)
community <- CardDeck$new(communitydeck, verbose = TRUE)
# if your chance cards different from mine,
# check to make sure sample(15) returns the following
# > set.seed(2)
# > sample(15)
#  [1]  5  6 14  8  1 11  9  2  3 10  7 12  4 13 15
```


```{r, error = TRUE}
player1 <- Player$new(verbose = TRUE)
monopoly <- SpaceTracker$new(verbose = TRUE)

for(i in 1:20){
  cat("--- Turn", i,"---\n")
  take_turn(player1, monopoly)
  cat("\n")
}

monopoly$counts
cbind(gameboard, counts = monopoly$counts)
```


# Part 2: 1000 simulated games

```{r, message = FALSE}
library(dplyr)
```


```{r, error = TRUE}
## Use non-verbose random dice for Part 2
set.seed(2)
chance <- CardDeck$new(chancedeck, verbose = FALSE)
community <- CardDeck$new(communitydeck, verbose = FALSE)
dice <- RandomDice$new()

player1 <- Player$new(verbose = FALSE)
player2 <- Player$new(verbose = FALSE)
monopoly <- SpaceTracker$new(verbose = FALSE)

for(g in 1:1000) {
  if(g %% 100 == 0) {
    cat("#### SIMULATING GAME", g, "##### \n")
  }
  for(i in 1:150){
    take_turn(player1, monopoly)
    take_turn(player2, monopoly)
  }
}

print(setNames(monopoly$counts, 1:40))
barplot(monopoly$counts)

results <- cbind(gameboard, tally = monopoly$counts)
results <- cbind(results, rel = monopoly$counts/sum(monopoly$counts))
print(results)

arrange(results, desc(tally))
```

